Title Goes Here\\ \large{Not For Redistribution}

### 2020-03-08 paper/paper.tex
Add 'not for redistribution' notice and adjust flowchart label
Possible GHC bug (somewhere, a call to (ga .) is failing and I never call it in this project). Probably related to the cast-float-over-app transformationgp

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Title Goes Here}

@@

\begin{itemize}
\item A representation of pattern matching in a Haskell EDSL (Section 3)
\item Representations of tail recursion (Section 4) and lambdas (Section 5) in
  the EDSL. We will see that lambdas become easier to implement once pattern
  matching and tail recursion already have EDSL representations.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section 7)
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section 6).
\end{itemize}

@@

@@

@@

If an expression already has an EDSL type (a type of the form \ttt{E a} for some
\ttt{a}), then the marking procedure ignores it and does not wrap it with
\ttt{externalize} (see $M$ in Section 7.2).

@@

In the following flowchart, the names in parentheses in a node refers to the names of transformations from the following section (Section 7.2).

@@

  \draw [arrow] (start) -- (tailrec);
  \draw [arrow] (tailrec) -- (findmark);
  \draw [arrow] (findmark) -- node[anchor=east] {Primitive} (handleprim);
  \draw [arrow] (findmark) -- node[anchor=west] {Function application/non-prim var} (handleapp);
  \draw [arrow] (findmark) -- node[anchor=east] {\ttt{case}} (handlecase);

@@

\clearpage
\section{Citations and Bibliographies}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Title Goes Here\\
\large{Not For Redistribution}}

@@

\begin{itemize}
\item A representation of pattern matching in a Haskell EDSL (Section 3)
\item Representations of tail recursion (Section 4) and lambdas (Section 5) in
  the EDSL. We will see that lambdas become easier to implement once pattern
  matching and tail recursion already have EDSL representations.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section 8)
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section 6).
\end{itemize}

@@

\begin{todo}
  Cite "Rewriting a Shallow DSL using a GHC Compiler Extension"
  (2017; Grebe, Young, Gill)
\end{todo}

@@

\section{C Backend}
\begin{todo}
  Write this section
\end{todo}

@@

If an expression already has an EDSL type (a type of the form \ttt{E a} for some
\ttt{a}), then the marking procedure ignores it and does not wrap it with
\ttt{externalize} (see $M$ in Section 8.2).

@@

In the following flowchart, the names in parentheses in a node refers to the names of transformations from the following section (Section 8.2).

@@

  \draw [arrow] (start) -- (tailrec);
  \draw [arrow] (tailrec) -- (findmark);
  \draw [arrow] (findmark) -- node[anchor=east] {Primitive} (handleprim);
  \draw [arrow] (findmark) -- node[anchor=west, yshift=0.1cm] {Function application/non-prim var} (handleapp);
  \draw [arrow] (findmark) -- node[anchor=east] {\ttt{case}} (handlecase);

@@

\clearpage
\section{Related Work}
\begin{todo}
  Cite and compare/contrast with pattern matching technique described in section
  3.3 of "Unembedding Domain-Specific Languages" (2009; Atkey, Lindley, Yallop)
\end{todo}

\section{Citations and Bibliographies}
